A thesis draft

### 2018-11-25 res/sections/15-ArchitecturalImplementation.tex
Add first attempt draft

\subparagraph*{Deployment via Docker Compose}
The deployment with Docker Compose tourned out to be best of the three
possibilities. Docker Compose configuration offered an unprecedented
configuration flexibility, with the possibility to deploy only selected modules.
On top of that, this method let us manage the Openbaton version freely, having
more control on update especially during the development of our components.
Finally, a Docker based solution seemed to be the best approach since all of our
components were meant to be put inside a Docker container.

>>>>

\subparagraph*{Deployment via Docker Compose}
The deployment with Docker Compose turned out to be best of the three
possibilities. The Docker Compose configuration offered an unprecedented
configuration flexibility, with the possibility to deploy only selected modules.
On top of that, this method let us manage the Openbaton version freely, having
more control on update especially during the development of our components.
Additionally, using this Docker Compose configuration allowed us to seamlessly
integrate the monitoring tools Zabbix, in order to have the possibility to
graphically see the data fetch from Openbaton about the system state. Finally, a
Docker based solution seemed to be the best approach since all of our components
were meant to be put inside a Docker container.

\subsection{Docker integration in Openstack}

\begin{figure}[t]
  \centering
  \includegraphics[scale=0.5]{dockeropenstackmodule}
  \caption[Docker module for Openstack working schema]{Docker module for Openstack
    working schema~\cite{openstackDockerModule}}
  \label{chap:archimpl:sec:fistattempt:img:dockeropnestackmodule}
\end{figure}

After the initial Openstack and Openbaton configuration we started making the
components talking to each other. First, we tried a simple \verb!iperf! data
transmission with two VNFs deployed by Openbaton as a common hypervisor-based
Openstack instances, as explained in~\cite{openbatonIperf}. With this test
completed, we started tinkering Openstack for using Docker containers instead of
traditional hypervisor instances. When we started developing this solution, we
adopted the Zun module, that aims to smoothly integrate Docker in Openstack.
Unfortunately, we were not able to make it properly work, in particular, it was
not possible to open selected desired ports on the Docker containers. This lead
to the impossibility to perform packet forwarding between VNFs. On top of that,
we found difficulties regarding the integration of Docker images in TOSCA
definitions and Openstack. These two issues are related: the TOSCA definition
does not have any keyword to specificate in any way that the image used for the
VNF definition is a Docker image, and Openstack, with the Zun plugin, at the
time of the implementation did not performed the image pull from any Docker
registry. The impossibility to easily set the containers port and the lack of
some support in between the TOSCA definition and the Openstack Zun plugin pushed
us to drop Openstack as a possible solution and to start looking for another
valid VIM component.
